Microxanox: an R package for simulating an aquatic \(MICR\)obial ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.

### 2023-06-02 inst/manuscript/Response.md

I have completed my evaluation of your manuscript. The reviewers recommend reconsideration of your manuscript following minor revision and modification. I invite you to resubmit your manuscript after addressing the comments below. Please resubmit your revised manuscript by Jun 12, 2023.

When revising your manuscript, please consider all issues mentioned in the reviewers' comments carefully: please outline every change made in response to their comments and provide suitable rebuttals for any comments not addressed. Please note that your revised submission may need to be re-reviewed.

To submit your revised manuscript, please log in as an author at <https://www.editorialmanager.com/softx/>, and navigate to the "Submissions Needing Revision" folder under the Author Main Menu.

SoftwareX values your contribution and I look forward to receiving your revised manuscript.

@@

Randall Sobie

Editor-in-Chief

SoftwareX

## Editor and Reviewer comments

### Reviewer #1

> 1. Please consider reference style: Number the references (numbers in square brackets) in the list in the order in which they appear in the text.

{>>Owen: Rainer - please correct and then make a response here.<<} {>>Rainer: Will do this at the end<<} *

> The authors in section 3.3 claim several sentences that could confuse readers.
2.1 `one discovers how the steady state of the system responds to the environmental conditions`. There are several concerns that the authors should clarify:
>
> a)  `The steady state`. Is there a unique steady state? Is there a reported contribution concerning a formal analysis of the model in the sense of stability (stable state existence and uniqueness)? Maybe, authors should refer as `a system's stable state (if it exists)`.

@@

**Response:** We removed this text and now simply state that having two methods allows the comparison of their results.

> 2.8 Please consider rewrite the section 3.3 (see previous 2.1 - 2.7 points) in the sense of Parametric sensitivity analysis, Open loop dynamical behavior, Equilibrium points (see Khalil, H. K. (2002). Nonlinear Systems. Prentice Hall, New Jersey.)

**Response:** we are of the opinion that the with the revisions already made and detailed above, and those below, that the terminology is now more in line with this text, and will be clearly understandable by the target audience (theoretical ecologists) even when the section is not completely rewritten.

> 3. Please consider the following suggestions:
>
> Line 5 `types of ecosystem`
